\documentclass[a4paper,14pt, ukrainian]{extarticle}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\usepackage[ukrainian]{babel}
\usepackage{graphicx} %Loading the package
\graphicspath{{images/}}
\usepackage[export]{adjustbox}
\usepackage{setspace}
\usepackage{mathtools}
\usepackage{float}
\usepackage{extsizes}

% \usepackage[utf8]{inputenc}
% \usepackage{mathptmx}




\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[dvipsnames]{xcolor}
\usepackage{bbm}
\numberwithin{equation}{section}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
% \usepackage[nottoc,numbib]{tocbibind}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{indentfirst} % отделять первую строку раздела абзацным отступом тоже
\usepackage{hyperref}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{fancyhdr}
\usepackage{tempora}
\usepackage{titlesec}

\usepackage{geometry}
\usepackage{enumitem}


\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}
\fancyheadoffset{0mm}
\fancyfootoffset{0mm}
\setlength{\headheight}{17pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addto\captionsukrainian{\def\refname{ПЕРЕЛІК ДЖЕРЕЛ ПОСИЛАНЬ}}
\addto\captionsukrainian{\renewcommand{\figurename}{Рисунок}}
\fancypagestyle{plain}{ 
    \fancyhf{}
    \rhead{\thepage}}

\newcommand{\sectionbreak}{\clearpage} % Кожна сеекція із нової сторінки

\titleformat{\chapter}[display]
    {\filcenter}
    {\MakeUppercase{\chaptertitlename} \thechapter}
    {8pt}
    {\bfseries}{}
 
\titleformat{\section}
    {\centering\normalsize\bfseries}
    {\thesection}
    {1em}{}
 
\titleformat{\subsection}
    {\normalsize\bfseries}
    {\thesubsection}
    {1em}{}
 
\geometry{left=3cm}
\geometry{right=1.5cm}
\geometry{top=2cm}
\geometry{bottom=2cm}
% Настройка вертикальных и горизонтальных отступов
\titlespacing*{\chapter}{0pt}{-30pt}{8pt}
\titlespacing*{\section}{\parindent}{*4}{*4}
\titlespacing*{\subsection}{\parindent}{*4}{*4}

\makeatletter
    \AddEnumerateCounter{\asbuk}{\@asbuk}{м)}
\makeatother
\setlist{nolistsep}
\renewcommand{\labelitemi}{-}
% \renewcommand{\labelenumi}{\asbuk{enumi})}
\renewcommand{\labelenumii}{\arabic{enumii})}

\tocloftpagestyle{empty}
\addto\captionsukrainian{%
  \renewcommand{\contentsname}{ЗМІСТ}%
}
\renewcommand{\cfttoctitlefont}{\hspace{0.5\textwidth}\bfseries}
\renewcommand{\cftbeforetoctitleskip}{1em}
% \renewcommand{\cftaftertoctitle}{\mbox{}\hfill \\ \mbox{}\hfill{\footnotesize Стр.}\vspace{-2.5em}}
\renewcommand{\cftsecfont}{\bfseries\hspace{31pt}}
\renewcommand{\cftsubsecfont}{\hspace{14pt}}
\renewcommand{\cftparskip}{-1mm}
\renewcommand{\cftdotsep}{1}
\setcounter{tocdepth}{2} % задать глубину оглавления — до subsection включительно


\makeatletter
    \renewcommand{\@dotsep}{2}
    \newcommand{\l@likechapter}[2]{{\bfseries\@dottedtocline{0}{0pt}{0pt}{#1}{#2}}}
\makeatother

% \newcommand{\likechapter}[1]{    
%     \likechapterheading{#1}    
%     \addcontentsline{toc}{likechapter}{\MakeUppercase{#1}}}

\useunder{\uline}{\ul}{}
\DeclareRobustCommand{\[}{\begin{equation}}
\DeclareRobustCommand{\]}{\end{equation}}
\counterwithin{figure}{section}
\counterwithin{table}{section}

\renewcommand{\cftsubsecaftersnum}{} % що буде писатися після номеру пункта (нічого)
\renewcommand{\cftsubsecindent}{3em} % відступ номера пункта від лівого краю
\renewcommand{\cftsubsecnumwidth}{2.5em} % розмір поля, що виділяється під номер пункта
\renewcommand{\cftsubsecpagefont}{\mdseries} % стиль номеру сторінки (звичайний, 14pt)
\renewcommand{\cftsubsecfont}{\mdseries} % стиль заголовку (звичайний)
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftsubsecdotsep}} % чим заповнювати проміжок від заголовку до номеру сторінки (точками)

\title{Оцінка якості моделей глибокого начання у системах рекомендацій}
\author{Володимир Малиняк}

\begin{document}

\input{sections/sk.tex}
\thispagestyle{empty}
\onehalfspacing
% \maketitlepage
\newpage
\tableofcontents
\input{sections/vstup.tex}
\input{sections/zagalni_poloz.tex}
\input{sections/dl_rec.tex}
\input{sections/metrics.tex}
\input{sections/alg.tex}
\input{sections/factors.tex}
\input{sections/datasets.tex}
\input{sections/experiments.tex}
\input{sections/end.tex}

\newpage
\begin{thebibliography}{99}
    \bibitem{NEUMF}
    Xiangnan He, Lizi Liao, Hanwang Zhang, Liqiang Nie, Xia Hu, and Tat-Seng Chua. 2017.  \emph{Neural Collaborative Filtering}. In Proceedings of the 26th International Conference on World Wide Web (WWW '17). International World Wide Web Conferences Steering Committee, Republic and Canton of Geneva, CHE, 173–182. https://doi.org/10.1145/3038912.3052569
    \bibitem{VAE}
    Dawen Liang, Rahul G. Krishnan, Matthew D. Hoffman, and Tony Jebara. 2018. \emph{Variational Autoencoders for Collaborative Filtering}. In Proceedings of the 2018 World Wide Web Conference (WWW '18). International World Wide Web Conferences Steering Committee, Republic and Canton of Geneva, CHE, 689–698. https://doi.org/10.1145/3178876.3186150
    \bibitem{NGCF}
    Xiang Wang, Xiangnan He, Meng Wang, Fuli Feng, and Tat-Seng Chua. 2019. \emph{Neural Graph Collaborative Filtering}. In Proceedings of the 42nd International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR'19). Association for Computing Machinery, New York, NY, USA, 165–174. https://doi.org/10.1145/3331184.3331267
    \bibitem{GraphBook}
    William L. Hamilton. (2020). \emph{Graph Representation Learning}. Synthesis Lectures on Artificial Intelligence and Machine Learning, Vol. 14, No. 3 , Pages 1-159.
    \bibitem{MetaRec}
    Le, James, "MetaRec: Meta-Learning Meets Recommendation Systems" (2020). Thesis. Rochester Institute of Technology.
    \bibitem{Metrics}
    Saúl Vargas. 2014. \emph{Novelty and diversity enhancement and evaluation in recommender systems and information retrieval}. In Proceedings of the 37th international ACM SIGIR conference on Research  development in information retrieval (SIGIR '14). Association for Computing Machinery, New York, NY, USA, 1281. https://doi.org/10.1145/2600428.2610382
    \bibitem{MetricPtoblems}
    Zhu Sun, Di Yu, Hui Fang, Jie Yang, Xinghua Qu, Jie Zhang, and Cong Geng. 2020. \emph{Are We Evaluating Rigorously? Benchmarking Recommendation for Reproducible Evaluation and Fair Comparison}. In Proceedings of the 14th ACM Conference on Recommender Systems (RecSys '20). Association for Computing Machinery, New York, NY, USA, 23–32. https://doi.org/10.1145/3383313.3412489
    \bibitem{RecoBook}
    Francesco Ricci, Lior Rokach, Bracha Shapira, and Paul B. Kantor. 2010. \emph{Recommender Systems Handbook (1st. ed.)}. Springer-Verlag, Berlin, Heidelberg.
    \bibitem{Bishop}
    Christopher M. Bishop. \emph{Pattern Recognition and Machine Learning}. 2006. ISBN-10: 0-387-31073-8. Springer New York, NY
    \bibitem{Colab}
    Google Colab [Електронний ресурс]. – Режим доступу:\href{https://colab.research.google.com/}{https://colab.research.google.com/}
    \bibitem{NetflixDataset}
    Netflix Prize Dataset [Електронний ресурс]. – Режим доступу:\href{https://archive.org/download/nfprize_dataset.tar}{https://archive.org/download/nfprize\_dataset.tar}
    \bibitem{MovilensDataset}
    Movilens Dataset [Електронний ресурс]. – Режим доступу:\href{https://grouplens.org/datasets/movielens/1m/}{https://grouplens.org/datasets/movielens/1m/}
    \bibitem{LastFMDataset}
    LastFM Dataset [Електронний ресурс]. – Режим доступу:\href{https://grouplens.org/datasets/hetrec-2011/}{https://grouplens.org/datasets/hetrec-2011/}
    \bibitem{Perceptron}
    Персептрон [Електронний ресурс]. – Режим доступу:\href{https://ru.wikipedia.org/wiki/%D0%9F%D0%B5%D1%80%D1%86%D0%B5%D0%BF%D1%82%D1%80%D0%BE%D0%BD}{https://ru.wikipedia.org/wiki/Перцептрон}
    \end{thebibliography}
\input{sections/dodatok1.tex}
\end{document}